---
title: "IAT Gender Career 2005"
author: "Alexander Porshnev"
date: "2023-08-21"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
library(knitr)
library(dplyr)
library(psych)

knitr::opts_chunk$set(echo = FALSE)
```

# Gender & Career experiment  IAT 2005-2022 (https://osf.io/abxq7/)

IAT task:

Female stimuli are: Rebecca, Michelle, Emily, Julia, Anna

Male stimuli are: Ben, Paul, Daniel, John, Jeffrey

Career stimuli are: Career, Corporation, Salary, Office, Professional, Management, Business

Family stimuli are: Wedding, Marriage, Parents, Relatives, Family, Home, Children


# Datasets & Variables

```{r download datasets}
setwd("C:/Alex/Maynooth/IAT/Gender-Career/Datasets/RAW_Preprocessed/2005")
#load participants data

p_data <- read.csv("Gender-Career IAT.public.2005.csv", header = TRUE, sep =",")
#load trial data
t_data <-read.csv("iat_2005.txt", header = TRUE, sep = "\t")

cook_data<-read.csv("cook_book.csv", header = FALSE,sep =",")

kable(dplyr::filter(cook_data, cook_data$V1%in%names(p_data)), caption = "Participants variables with D, Mean RT, etc.", col.names = c("Name","Comment"))

kable(names(t_data), caption = "Long dataset (variables for each trial)", col.names = "")

kable(rbind(
  c("Np - participants in Gender-Career IAT.public.2005.csv", length(p_data$session_id)),
  c("Nt - trials in iat_2005.txt", length(t_data$session_id)),    c("trials per participant", 200), 
  c("expected Np*200 ", length(p_data$session_id)*200),
  c("missing", length(p_data$session_id)*200 - length(t_data$session_id) )
            ), caption = "N in datasets")
```
# Check mean RT times calculations
```{r RT calculations}
res <- t_data %>% filter(block_number == 2) %>% group_by(session_id) %>% summarize(M_block3 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_3' )], res, by)
kable(head(check_data), caption = "RT - block 3")

res <- t_data %>% filter(block_number == 3) %>% group_by(session_id) %>% summarize(M_block4 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_4' )], res, by)
kable(head(check_data), caption = "RT - block 4")

res <- t_data %>% filter(block_number == 5) %>% group_by(session_id) %>% summarize(M_block6 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_6' )], res, by)
kable(head(check_data), caption = "RT - block 6")

res <- t_data %>% filter(block_number == 6) %>% group_by(session_id) %>% summarize(M_block7 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_7' )], res, by)
kable(head(check_data), caption = "RT - block 6")

res <- t_data %>% filter(block_number %in% c(2,3,5,6)) %>% group_by(session_id) %>% summarize(M_block3467 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_3467' )], res, by)
kable(head(check_data), caption = "RT - blocks 3467")
```


# Participants' countries available

```{r Countries}
kable(head(sort(table(p_data$countryres), decreasing = TRUE),10), caption = "Top 10 participants' countries")
```

# Description of UK participants

```{r , results = 'asis'}
p_UK<- filter(p_data, countryres=="UK")
kable(table(!is.na(p_UK$D_biep.Male_Career_all)), caption = "Number of UK participants with D calculated ")

p_UK_clean<- filter(p_UK, !is.na(D_biep.Male_Career_all))
kable(table(p_UK_clean$sex), caption = "UK participans (with D calculated): Disribution by gender")


p_UK_clean<- filter(  p_UK, !is.na(D_biep.Male_Career_all) & 
                      countryres=="UK" & 
                      p_UK$sex %in% c("m","f"))
t_UK_clean<- filter(t_data, session_id %in% p_UK_clean$session_id)

res_err <- t_UK_clean %>% filter(block_number %in% c(2,3,5,6)) %>% group_by(session_id) %>% summarize(errors = sum(trial_error), n = n())
res_err$PCT_3467<-res_err$errors/res_err$n*100


by <- join_by(session_id)
check_data<-right_join(p_data[c("session_id", 'PCT_error_3467')], res_err, by)
kable(head(check_data), caption = "Top 10, no differences occur")

kable(table(check_data$errors<12), caption = "Errors rate lower than 10%") #errors rate 10%

hist(log(p_UK_clean$Mn_RT_all_3467), n =30)

kable(describe(check_data$errors), caption = "Errors in blocks 3,4,6,7")

p_UK_clean$log_RT3467<-log(p_UK_clean$Mn_RT_all_3467) # probably we need to remove outliers 323ms (has many errors) and 2100ms (probably can keep) Greenwald et al. have frame 300ms to 3000ms (and trucate all ouliers to the boundaries) 
#kable(table(p_UK_clean$log_RT3467<6 | p_UK_clean$log_RT3467>7.5), caption = "Outliers -  log_RT3467<6 and p_UK_clean$log_RT3467>7.5 (Mean RT)")
#p_UK_clean$Mn_RT_all_3467[p_UK_clean$log_RT3467<6 | p_UK_clean$log_RT3467>7.5]

kable(describe(p_UK_clean$Mn_RT_all_3467), caption = "Mean Reaction time for blocks 3,4,6,7")

#age exclude participants <18
#education 1. elementary school, 2 junior high - exclude
#important variable country Country/Region of Primary Citizenship probably we should focus on it
# countrycit + variable  countrycit==countryres?

p_UK_clean<- filter(  p_UK, !is.na(D_biep.Male_Career_all) & 
                      countryres=="UK" & 
                      p_UK$sex %in% c("m","f") &
                      !( log(p_UK$Mn_RT_all_3467)<6| log(p_UK$Mn_RT_all_3467)>7.5 ) &
                      p_UK$PCT_error_3467 <= 10 &
                      p_UK$age>17)

t_UK_clean<- filter(t_data, session_id %in% p_UK_clean$session_id)

# added new variable - migration, than Country of residence "UK" not the country of origin "all others"
p_UK_clean$country_mig<-p_UK_clean$countrycit!="UK"
c_vars= c('sex', 'Order', 'politicalid_6', "country_mig")
c_vars_exp = c('edu', 'ethnic', "major")
n_vars=c('age', 'Mn_RT_all_3467', 'PCT_error_3467', 'D_biep.Male_Career_all')
i="country_mig"
for (i in c_vars){
  print(kable(table(p_UK_clean[,i]), caption = i))}

for (i in c_vars_exp){
  cook_data<-read.csv(paste0("cook_book_", i,".csv"), header = FALSE,sep =",")
  by<-join_by("Var1", "V1")
  res<-left_join(as.data.frame(table(p_UK_clean[,i])), cook_data, by = c("Var1" = "V1"))
  names(res)<-c("Value", "Freq", "Category")
  print(kable(res), caption = i)
  }

kable(describe(p_UK_clean[,n_vars]), caption = "Numeric variables")
# No data to connect sessions - previous_session_id
# No data to connect user_id 

exp_vars = c("assocareer",
"assofamily",
"impcareer",
"impfamily",
"havechildren",
"numboys",
"numgirls",
"planchildren")
kable(describe(p_UK_clean[,exp_vars]), caption = "Explicit attitudes variables")

write.csv(p_UK_clean, "p_UK_clean.csv", row.names = FALSE)
write.csv(t_UK_clean, "t_UK_clean.csv", row.names = FALSE)

```
```{r, results= 'asis'}
d_calculations<- function(t_data, p_data, block1, block2,d_var = "D_biep.Male_Career_36"){

res1 <- t_data %>% filter(block_number %in% block1) %>% group_by(session_id) %>% summarize(M_block1 = mean(trial_latency), )

res2 <- t_data %>% filter(block_number %in% block2) %>% group_by(session_id) %>% summarize(M_block2 = mean(trial_latency), )

res12sd <- t_data %>% filter(block_number %in% c(block1, block2)) %>% group_by(session_id) %>% summarize(sd12 = sd(trial_latency))

by = join_by(session_id)
check_data<-left_join(res1, res2, by)
check_data<-left_join(check_data, res12sd, by)
check_data$D<-(check_data$M_block1-check_data$M_block2)/(check_data$sd12)
p_data$order_sign<- ifelse(p_data$Order==2,1,-1)

check_data_res<-left_join(p_data[,c("session_id", d_var, "order_sign" )], check_data[,c("D", "session_id")], by)
check_data_res$D<-check_data_res$D*check_data_res$order_sign
check_data_res<-check_data_res[,-3] #remove additional sign column

print(kable(head(check_data_res), caption = paste0("Similar values (top 10) from ",
                                                   table(check_data_res$D-check_data_res[, c(d_var)]<0.01)[2])
            ))

#print(kable(table(check_data_res$D-check_data_res[, c(d_var)]<0.01), caption = "Cross-tab similar vs different values"))
print(kable(head(check_data_res[((check_data_res$D-check_data_res[,c(d_var)])>0.01),]), caption = paste0(" Differences, top 10  from ",  
table(check_data_res$D-check_data_res[, c(d_var)]<0.01)[1])))
return (check_data_res)
}
```


# D - comparison  
D_biep.Male_Career - variable calculated for each participant in pre-processed file
D - calculated from raw data (M1- M2)/sd(12)

```{r, results= 'asis'}
print("Block 3 vs 6")
d1 <- d_calculations(t_UK_clean, p_UK_clean, c(2), c(5))
print("Block 4 vs 7")
d2 <- d_calculations(t_UK_clean, p_UK_clean, c(3), c(6), d_var = "D_biep.Male_Career_47")
print("Blocks 3&4 vs 6&7")
d3<-d_calculations(t_UK_clean, p_UK_clean, c(2,3), c(6,5), d_var = "D_biep.Male_Career_all")
names(d3)[3]<-"D_3467"
by = join_by(session_id)
check_data_res<-left_join(d1, d2, by)
check_data_res<-left_join(d3, check_data_res, by)

check_data_res$D_mean<-(check_data_res$D.x+check_data_res$D.y)/2

print("Correlation D_biep.Male_Career_all & D_3467")
print(cor(check_data_res$D_biep.Male_Career_all, check_data_res$D_3467))
kable(head(check_data_res[,c("D_biep.Male_Career_all","D_mean","D_3467")]), caption = "Comparison of original D and Dmean from calculations")
print(kable(head(check_data_res[((check_data_res$D_mean-check_data_res[,c("D_biep.Male_Career_all")])>0.01),]), caption = paste0(" Differences, top 10  from ",  
table(check_data_res$D_mean-check_data_res[, c("D_biep.Male_Career_all","D_mean","D_3467")]<0.01)[1])))

```
# Whole dataset D calculations (D_biep.Male_Career_all - NA removed)

```{r results='asis'}
p_data_NAN <- filter(p_data, !is.na(p_data$D_biep.Male_Career_all))
print("Block 3 vs 6")
d1 <- d_calculations(t_data, p_data_NAN, c(2), c(5))
print("Block 4 vs 7")
d2 <- d_calculations(t_data, p_data_NAN, c(3), c(6), d_var = "D_biep.Male_Career_47")
print("Blocks 3&4 vs 6&7")
d3<-d_calculations(t_data, p_data_NAN, c(2,3), c(6,5), d_var = "D_biep.Male_Career_all")
names(d3)[3]<-"D_3467"
by = join_by(session_id)
check_data_res<-left_join(d1, d2, by)
check_data_res<-left_join(d3, check_data_res, by)

check_data_res$D_mean<-(check_data_res$D.x+check_data_res$D.y)/2

cor(check_data_res$D_biep.Male_Career_all, check_data_res$D_3467)
kable(head(check_data_res[,c("D_biep.Male_Career_all","D_mean","D_3467")]), caption = "Comparison of original D and Dmean from calculations")
print(kable(head(check_data_res[((check_data_res$D_mean-check_data_res[,c("D_biep.Male_Career_all")])>0.01),]), caption = paste0(" Differences, top 10  from ",  
table(check_data_res$D_mean-check_data_res$D_biep.Male_Career_all<0.01)[1])))
#kable(table(is.na(check_data_res$D_biep.Male_Career_all)), caption = "Number of is NA")
```
