---
title: "IAT Gender Career 2005"
author: "Alexander Porshnev"
date: "2023-08-02"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
library(knitr)
library(dplyr)
library(psych)

knitr::opts_chunk$set(echo = FALSE)
```

# Gender & Career experiment  IAT 2005-2022 (https://osf.io/abxq7/)

IAT task:

Female stimuli are: Rebecca, Michelle, Emily, Julia, Anna

Male stimuli are: Ben, Paul, Daniel, John, Jeffrey

Career stimuli are: Career, Corporation, Salary, Office, Professional, Management, Business

Family stimuli are: Wedding, Marriage, Parents, Relatives, Family, Home, Children


# Datasets & Variables

```{r download datasets}
setwd("C:/Alex/Maynooth/IAT/Gender-Career/Datasets/RAW_Preprocessed/2005")
#load participants data

p_data <- read.csv("Gender-Career IAT.public.2005.csv", header = TRUE, sep =",")
#load trial data
t_data <-read.csv("iat_2005.txt", header = TRUE, sep = "\t")

kable(names(p_data), caption = "Participants dataset variables", col.names = "")

kable(names(t_data), caption = "TRIAL dataset variables", col.names = "")

kable(rbind(
  c("Np - participants in Gender-Career IAT.public.2005.csv", length(p_data$session_id)),
  c("Nt - trials in iat_2005.txt", length(t_data$session_id)),    c("trials per participant", 200), 
  c("expected Np*200 ", length(p_data$session_id)*200),
  c("missing", length(p_data$session_id)*200 - length(t_data$session_id) )
            ), caption = "N in datasets")
```
# Check mean RT times calculations
```{r RT calculations}
res <- t_data %>% filter(block_number == 2) %>% group_by(session_id) %>% summarize(M_block3 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_3' )], res, by)

res <- t_data %>% filter(block_number == 3) %>% group_by(session_id) %>% summarize(M_block4 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_4' )], res, by)

res <- t_data %>% filter(block_number == 5) %>% group_by(session_id) %>% summarize(M_block6 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_6' )], res, by)

res <- t_data %>% filter(block_number == 6) %>% group_by(session_id) %>% summarize(M_block7 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_7' )], res, by)

res <- t_data %>% filter(block_number %in% c(2,3,5,6)) %>% group_by(session_id) %>% summarize(M_block3467 = mean(trial_latency))
by <- join_by(session_id)
check_data<-left_join(p_data[,c('session_id', 'Mn_RT_all_3467' )], res, by)
```

# Check D calculations 

```{r calculation D}
#mean for devided by sd 

res3 <- t_data %>% filter(block_number == 2) %>% group_by(session_id) %>% summarize(M_block3 = mean(trial_latency))
res6 <- t_data %>% filter(block_number == 5) %>% group_by(session_id) %>% summarize(M_block6 = mean(trial_latency))
res36sd <- t_data %>% filter(block_number %in% c(2,5)) %>% group_by(session_id) %>% summarize(sd36 = sd(trial_latency))

by <- join_by(session_id)
check_data<-left_join(res3, res6, by)
check_data<-left_join(check_data, res36sd, by)
check_data$D<-(check_data$M_block3-check_data$M_block6)/check_data$sd36

head(check_D<-left_join(p_data[,c('session_id', 'D_biep.Male_Career_36' )], check_data, by))
```

# Check if UK participants available

```{r UK participants}
kable(head(sort(table(p_data$countryres), decreasing = TRUE),10), caption = "Top 10 participants' countries")
p_UK<- filter(p_data, countryres=="UK")
kable(table(!is.na(p_UK$D_biep.Male_Career_all)), caption = "Number of participants with D calculated ")
p_UK_clean<- filter(p_UK, !is.na(D_biep.Male_Career_all))
kable(table(p_UK_clean$sex), caption = "Disribution by gender: UK participans& D calculated")
```

# Description of UK participants

```{r , results = 'asis'}
p_UK_clean<- filter(  p_UK, !is.na(D_biep.Male_Career_all) & 
                      countryres=="UK" & 
                      p_UK$sex %in% c("m","f"))
t_UK_clean<- filter(t_data, session_id %in% p_UK_clean$session_id)

res_err <- t_UK_clean %>% filter(block_number %in% c(2,3,5,6)) %>% group_by(session_id) %>% summarize(errors = sum(trial_error), n = n())
res_err$PCT_3467<-res_err$errors/res_err$n*100


by <- join_by(session_id)
check_data<-right_join(p_data[c("session_id", 'PCT_error_3467')], res_err, by)
kable(head(check_data))

kable(table(check_data$errors<12)) #errors rate 10%
hist(log(p_UK_clean$Mn_RT_all_3467), n =30)
kable(describe(check_data$errors), caption = "Errors in blocks 3,4,6,7")

p_UK_clean$log_RT3467<-log(p_UK_clean$Mn_RT_all_3467) # probably we need to remove outliers 323ms (has many errors) and 2100ms (probably can keep) 
kable(table(p_UK_clean$log_RT3467<6 | p_UK_clean$log_RT3467>7.5))
p_UK_clean$Mn_RT_all_3467[p_UK_clean$log_RT3467<6 | p_UK_clean$log_RT3467>7.5]
kable(describe(p_UK_clean$Mn_RT_all_3467), caption = "Mean Reaction time for blocks 3,4,6,7")

#age exclude participants <18
#education 1. elementary school, 2 junior high - exclude
#important variable country Country/Region of Primary Citizenship probably we should focus on it
# countrycit + variable  countrycit==countryres?

p_UK_clean<- filter(  p_UK, !is.na(D_biep.Male_Career_all) & 
                      countryres=="UK" & 
                      p_UK$sex %in% c("m","f") &
                      !( log(p_UK$Mn_RT_all_3467)<6| log(p_UK$Mn_RT_all_3467)>7.5 ) &
                      p_UK$PCT_error_3467 <= 10 &
                      p_UK$age>17)
t_UK_clean<- filter(t_data, session_id %in% p_UK_clean$session_id)
p_UK_clean$country_mig<-p_UK_clean$countrycit!="UK"
c_vars= c('sex', 'Order', 'edu', 'ethnic', 'politicalid_6', "country_mig", "major")
n_vars=c('age', 'Mn_RT_all_3467', 'PCT_error_3467')

for (i in c_vars){
  print(kable(table(p_UK_clean[,i]), caption = i))}


kable(describe(p_UK_clean[,n_vars]), caption = "Numeric variables")
# No data to connect sessions - previous_session_id
# No data to connect user_id 

exp_vars = c("assocareer",
"assofamily",
"impcareer",
"impfamily",
"havechildren",
"numboys",
"numgirls",
"planchildren")
kable(describe(p_UK_clean[,exp_vars]), caption = "Explicit attitudes variables")
```

