---
title: "Report_on_cleaning_raw_data"
author: "Alexander Porshnev"
date: "2023-10-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis', warning = FALSE)
library(dplyr)
library(knitr)
library(psych)
library(md.log)
library(data.table)
library(tidyr)
```

## Thresholds for data clearning

200ms < RT  

M1 M2 (+-3SD) per participant per condition 

Threshold for errors in session err_rate<30% 

Error rate – analysis (add variable error_rate) run whole analysis for participants with err_rate< 10%, check if the results are similar for the whole sample. 

Go throught all datasets – unify values (m,f, 0,1, etc.), normalize names (birth_sex), filter RT outliers, add error_rate  variable 

```{r main, echo = FALSE, results = 'asis', warning = FALSE}
year=2005
path = "C:\\Alex\\Maynooth\\IAT\\Gender-Career\\Analysis\\"
t_filename = paste0(path, "Sep23_stage2_All_years\\Clean_datasets\\t_", year, ".csv")
t_data_d <- fread(t_filename)

total <- length(unique(t_data_d$session_id))
total_trials <- nrow(t_data_d) 
print(paste0("Number of participants In total in pre-clean dataset: ", total))  
print(paste0("Number of trials In total in pre-clean dataset: ", total_trials))  
t_data_d$quick_trial<- t_data_d$trial_latency < 200
t_data_s <- t_data_d %>% filter(!quick_trial) 
total_trials_200 <- nrow(t_data_s) 
print(paste0("Number of trials In total in pre-clean dataset: ", total_trials, "After > 200ms:", total_trials_200," , removed: ",total_trials-total_trials_200, " in %: ", round((total_trials-total_trials_200)/total_trials, 3)  ))

t_data_err_rate <- t_data_d %>% group_by(session_id) %>% summarise(err_rate = sum(trial_error)/n())

kable(table(t_data_err_rate$err_rate<0.3), caption = "Number of participants with error rate <30%")

high_err_rate <-t_data_err_rate %>% filter(err_rate<0.3) %>% select(session_id) %>% unique()

t_data_d$high_err_rate <- t_data_d$session_id %in% high_err_rate$session_id

table(t_data_d$high_err_rate)

kable(table(t_data_err_rate$err_rate<0.2), caption = "Number of participants with error rate <20%")

kable(table(t_data_err_rate$err_rate<0.1), caption = "Number of participants with error rate <10%")

t_data_d$s<-NA
t_data_d <- t_data_d %>% mutate(ID = row_number())

t_data_m1 <- t_data_d %>% filter(block_number %in%c(2,3))%>% group_by(session_id) %>% summarise(M1 = mean(trial_latency), three_sd1 = 3*sd(trial_latency))

t_data_out_lier23 <- t_data_d %>% filter(block_number %in%c(2,3)) %>% select(session_id, trial_latency, ID) %>%  left_join(t_data_m1)
t_data_out_lier23$outlier<-(t_data_out_lier23$trial_latency<t_data_out_lier23$M1-t_data_out_lier23$three_sd1 | t_data_out_lier23$trial_latency>t_data_out_lier23$M1 +t_data_out_lier23$three_sd1)

kable(table(!t_data_out_lier23$outlier), caption = "Number of trials in 3sd interval of RT in blocks 3,4")                         

outlier_23 <- t_data_out_lier23 %>% filter(outlier) %>% select(ID)

t_data_m2 <- t_data_d %>% filter(block_number %in%c(5,6))%>% group_by(session_id) %>% summarise(M2 = mean(trial_latency), three_sd2 = 3*sd(trial_latency))
t_data_out_lier56 <- t_data_d %>% filter(block_number %in%c(5,6)) %>% select(session_id, trial_latency, ID) %>%  left_join(t_data_m1)
t_data_out_lier56$outlier<-(t_data_out_lier56$trial_latency<t_data_out_lier56$M1-t_data_out_lier56$three_sd1 | t_data_out_lier56$trial_latency>t_data_out_lier56$M1 +t_data_out_lier56$three_sd1)
kable(table(!t_data_out_lier56$outlier), caption = "Number of trials in 3sd interval of RT in blocks 6,7")                         

outlier_56 <- t_data_out_lier56 %>% filter(outlier) %>% select(ID)

t_data_d$trial_error_RT <- (t_data_d$ID %in%  c(outlier_23$ID, outlier_56$ID))

kable(table(t_data_d$trial_error_RT), caption = "Number of trials with RT outliers (RT<M-3s or RT>M+3sd)")

t_data_clean <- t_data_d %>% filter (!trial_error_RT & !quick_trial & !high_err_rate) 

print(paste0("We need to exclude: ", nrow(t_data_clean), " from our trials, so remove %:", round(nrow(t_data_clean)/ nrow(t_data_d), 3)))

print(paste0("In total we have: ",length(unique(t_data_d$session_id)), " and need to exclude: ", length(unique(t_data_clean$session_id)), " from our participants, so remove %:", round(length(unique(t_data_clean$session_id))/ length(unique(t_data_d$session_id)),3)))
```




md.log("Start", file="log.txt", append =FALSE, time = TRUE)
i=2005

for (i in 2005:2005){
  md.log(paste0("year", i, "started"))
  cat(paste0("\n# ", i, "\n"))
  describe_clean_data_RT(i)
  md.log(paste0("year", i, "done"))
}

