---
title: 'LDM: IAT Gender&Career Project Figures and Tables'
author: "Alexander Porshnev"
date: "2024-10-29"
output: html_document
---

```{r setup, include=FALSE}
library(data.table)
library(dplyr)
library(knitr)
library(ggplot2)
library(cowplot)
library(stringr)
library(patchwork)
#library(gridExtra)

knitr::opts_chunk$set(echo = FALSE, asis = TRUE)
#setwd()
#
#path<-"C:/Alex/Maynooth/IAT/Gender-Career/Analysis/git_for_replication/S3_5_full_check/"
#setwd("C:/Alex/Maynooth/IAT/Gender-Career/Analysis/Jul24_stage4/")
#start_year<-2019
#finish_year<-2019
#model_type<-"classic"

path_out_figures<-paste0(path, "/Step_05/out_05_Summary_", model_type,"/", start_year,"-", finish_year,"/")

dir_structure<-c(paste0("/Step_05/out_05_Summary_", model_type), paste0("/Step_05/out_05_Summary_", model_type,"/",start_year,"-", finish_year,"/"))

for (d in dir_structure){
dir.create(file.path(path, d), showWarnings = TRUE)
}
```

```{r additional function}
table_out <- function(d, c_text, transform = 1){
  if (transform == 1){
    kable(table(d), col.names = NULL, caption = c_text)}
  else{
    kable(d, col.names = NULL, caption = c_text)}
}

getBIC <- function (df_BIC, corpora_name, sample_name ){
  res<-unname(d_BIC %>% filter(corpora == corpora_name, sample == sample_name) %>% select(BIC))
  return(res[[1]])
}
```



```{r Reading&Transforming data from modelling output}
#Reading data from modelling output for sample A&B
model_type="classic"
dA<- fread(paste0(path,"/Step_04/out_4_Summary_classic/", start_year,"-", finish_year,"/Summary_table_",start_year,"_", finish_year, "_A_", model_type,".csv"))

#View(dA)
dA$ext_model<-paste0(dA$lmd, dA$baseline)

dB<- fread(paste0(path,"/Step_04/out_4_Summary_classic/", start_year,"-", finish_year,"/Summary_table_",start_year,"_", finish_year,"_B_",  model_type,".csv"))
dB$ext_model<-paste0(dB$lmd, dB$baseline)

dR<- left_join(dA, dB, by = join_by("ext_model" == "ext_model"), suffix = c("_A", "_B"))

#Tranforming data to simplify report process
dR$corpora<-NA
dR$corpora[grep("logUKWAC",dR$baseline_A)]<-"ukwac"
dR$corpora[grep("logSUBTITLES",dR$baseline_A)]<-"subtitles"
dR$corpora[grep("logBNC",dR$baseline_A)]<-"bnc"

dR$measure<-NA
dR$measure[grep("ngram",dR$lmd_A)]<-"-"
dR$measure[grep("cos_",dR$lmd_A)]<-"cos"
dR$measure[grep("euc_",dR$lmd_A)]<-"euc"
dR$measure[grep("cor_",dR$lmd_A)]<-"cor"

dR$stimuli<-"lowercase"
dR$stimuli[grep("pairs_names_Upper",dR$lmd_A)]<-"capitalized"


llms<-c("_llama_2_13b_Q8_0",                "_llama_2_70b_Q5_0",               
  "_llama_2_7b_Q8_0",                 "_llama_30b_Q8_0",                 
 "_llama_65b_Q5_0",                  "_llama_7b_Q8_0",                  
 "_Meta_Llama_3_1_70B_Q5_K_M",      "_meta_llama_3_1_8b_q8_0" ,        
  "_mistral_7b_v0_1_Q8_0",            "_Mistral_7B_v0_3_Q8_0" ,          
 "_dolphin_2_8_mistral_7b_v02_Q8_0", "_Hermes_3_Llama_3_1_70B_Q5_K_M" )

classic<- c("_cbow",
"_skipgram",
"_probability_ratios_None",
"_log_cooccurrence_None",
"_pmi_None",
"_ppmi_None",
"_conditional_probability_ngram",
"_conditional_probability_None",
"_log_ngram_freq",
"_ppmi_ngram",
"_probability_ratio_ngram",
"_pmi_ngram",
"_glove_6B_300d","_glove_42B_300d","_GoogleNews_vectors_negative300",
"_log_ngram")


mdls<-c(llms, classic)
      
      

mdls_s<-sub('.', '', mdls)
dR$model<-NA
i<-1
for (i in 1:length(mdls)){
  dR$model[grep(mdls[i],dR$lmd_A)]<-mdls_s[i]
}
table_out(!is.na(dR$model), "Model check")
table_out(dR$model, "Models")

pretrained<-c(llms, "_glove_6B_300d")
dR$pretrained<-0
for (i in 1:length(pretrained)){
  dR$pretrained[grepl(pretrained[i],dR$lmd_A)]<-1
}
table(dR$pretrained)


rds<-c("_r1",
        "_r10",
        "_r5",
        "_r3")

rds_s<-c("r_01",
              "r_10",
              "r_05",
              "r_03")

dR$window_radius<-"-"
for (i in 1:length(rds)){
  dR$window_radius[grep(rds[i],dR$lmd_A)]<-rds_s[i]
}
gloves<-c("_glove_42B_300d", "_glove_6B_300d")
for (i in gloves){
  dR$window_radius[grep(i,dR$lmd_A)]<-"r_global"}

dR$window_radius[grep("_GoogleNews_vectors_negative300",dR$lmd_A)]<-"na"


for (i in 1:length(llms)){
  dR$window_radius[grep(llms[i],dR$lmd_A)]<-"r_4096"
}

table_out(dR$window_radius, "Window radius")

dR$embedding_size<-"None"
embs<-c("_50",
       "_100",
       "_200",
       "_300",
       "_500")
embs_s<-sub('.', '', embs)

for (i in 1:length(embs_s)){
  dR$embedding_size[grep(embs_s[i],dR$lmd_A)]<-embs_s[i]
}

for (i in gloves){
dR$embedding_size[grep(i,dR$lmd_A)]<-"300"}
#dR$embedding_size[grep("_llama_2_7b_chat_Q4_K_M",dR$lmd_A)]<-"4096"
#dR$embedding_size[grep("_mistral_7b_v0_1_Q4_K_M",dR$lmd_A)]<-"4096"
#dR$embedding_size[grep("_llama_2_13b_chat_Q5_K_S",dR$lmd_A)]<-"5120"

table_out(dR$embedding_size, "Embedding size")
llm_list<-cbind(llms, rep("llm",length(llms)))

t_mdls<-rbind(c("_cbow","predict"),
          c("_skipgram","predict"),
          llm_list,
          c("_probability_ratios_None","count"),
          c("_log_cooccurrence_None","count"),
          c("_pmi_None","count"),
          c("_ppmi_None","count"),
          c("_conditional_probability_None","count"),
          c("_conditional_probability_ngram","ngram"),
          c("_log_ngram","ngram"),
          c("_ppmi_ngram","ngram"),
          c("_probability_ratio_ngram","ngram"),
          c("_pmi_ngram","ngram"),
          c("_glove_6B_300d","count"),
          c("_glove_42B_300d","count"),
          c("_GoogleNews_vectors_negative300", "predict")
                    )
t_mdls<-as.data.frame(t_mdls)
name<-sub('.', '', t_mdls$llms)
t_mdls$name<-name

dR$family<-NA
for (i in 1:length(t_mdls$name)){
  dR$family[grep(t_mdls[i,1],dR$lmd_A)]<-t_mdls[i,2]
}
table(dR$family, dR$model) 

dR$case<-"Lower"
dR$case[grepl("Upper",dR$lmd_A)]<-"Captzd"

```

```{r adding BIC }

# BIC baseline calculated in previous steps

d_BIC<-read.csv(paste0(path,"/Step_03/out_3_EXT_RT/",start_year,"-", finish_year,"/BIC_", start_year,"_", finish_year,"_",model_type, ".csv"))
d_BIC$corpora<-NA
d_BIC$corpora[grep("logUKWAC", d_BIC$model)] <-"ukwac"
d_BIC$corpora[grep("logBNC", d_BIC$model)] <-"bnc"
d_BIC$corpora[grep("logBBC", d_BIC$model)] <-"subtitles"

dR$base_BIC_A<-NA

dR$base_BIC_A[dR$corpora == "bnc"]<-  getBIC(d_BIC, "bnc", "A") #1178.2
dR$base_BIC_A[dR$corpora == "subtitles"]<- getBIC(d_BIC, "subtitles", "A") #1180.82
dR$base_BIC_A[dR$corpora == "ukwac"]<-getBIC(d_BIC, "ukwac", "A") #1177.56

dR$base_BIC_B<-NA
dR$base_BIC_B[dR$corpora == "bnc"]<-getBIC(d_BIC, "bnc", "B") #1179.41
dR$base_BIC_B[dR$corpora == "subtitles"]<-getBIC(d_BIC, "subtitles", "B") #1182.06
dR$base_BIC_B[dR$corpora == "ukwac"]<-getBIC(d_BIC, "ukwac", "B") #1178.74
```


#### Creating summary tables for conditions
##### C1_corr_dir: direction of correlations between LDM and m_RT is similar at the both samples A and B
##### C0_bAB: sign of estimate for LDM in regression model for m_RT is similar at the both samples A and B: direction of correlations between LDM and m_RT is similar at the both samples A and B
##### C2_B_inCI: Correlation between LDM and m_RT on sample B is in C.I. obtained from sample A
##### C3_AB_pvalue: p-values for estimate for LDM in regression model for m_RT are less than 0.05 on the both samples
##### C1C2C3: C1_corr_dir AND C2_B_inCI AND C3_AB_pvalue
##### C4_dBIC_AB: decrease of BIC in comparison LDM regression model and baseline is more than 3 for at the both samples
##### C1C2C3C4: C1_corr_dir AND C2_B_inCI AND C3_AB_pvalue AND C4_dBIC_AB

```{r Conditions}

t<-table(dR$family)


dR$C1_corr_dir<- (dR$corLDMmRT_A*dR$corLDMmRT_B)>0
dR$C0_bAB<- (dR$coef_A*dR$coef_B)>0

dR$C2_B_inCI <-(dR$corLDMmRT_B<dR$corLDMmRT_CI_upper_A)&(dR$corLDMmRT_B>dR$corLDMmRT_CI_lower_A)

dR$C1C2<-dR$C1_corr_dir&dR$C2_B_inCI

dR$C3_AB_pvalue<-(dR$p_value_A<0.05)&(dR$p_value_B<0.05)

dR$C1C2C3<-dR$C1_corr_dir&dR$C2_B_inCI&dR$C3_AB_pvalue

dR$C4_dBIC_AB <-((-dR$BIC_A + dR$base_BIC_A)>3)&((-dR$BIC_B + dR$base_BIC_B)>3)

dR$C1C2C3C4<-dR$C1_corr_dir & dR$C2_B_inCI & dR$C3_AB_pvalue & dR$C4_dBIC_AB


r<-dR %>% group_by(family, model) %>% summarise(n= n(), 
                                                C0_bAB = sum(C0_bAB),
                                                C0_bABpc = sum(C0_bAB)/n()*100,
                                                C1 = sum(C1_corr_dir),
                                                C1pc = sum(C1_corr_dir)/n()*100,
                                                C2 = sum(C2_B_inCI),
                                                C2pc = sum(C2_B_inCI)/n()*100,
                                                C3 = sum(C3_AB_pvalue),
                                                C3pc = sum(C3_AB_pvalue)/n()*100,
                                                C4 = sum(C4_dBIC_AB),
                                                C4pc = sum(C4_dBIC_AB)/n()*100,
                                                C3C4 = sum(C4_dBIC_AB&C3_AB_pvalue),
                                                                             
                                                C3C4pc = sum(C4_dBIC_AB&C3_AB_pvalue)/n()*100,
                                                allC = sum(C0_bAB& C4_dBIC_AB&C3_AB_pvalue),
                                                allCpc = sum(C0_bAB& C4_dBIC_AB&C3_AB_pvalue)/n()*100, .groups = 'drop')

table_out(table(dR$C0_bAB, dR$C3_AB_pvalue), "Condition 0 x Condition C3")
table_out(table(dR$C0_bAB, dR$C4_dBIC_AB), "Condition 0 x Condition C4")

table_out(table(dR$C3_AB_pvalue, dR$C4_dBIC_AB), "Condition 3 x Condition C4")


t<-dR %>% group_by(family) %>% summarise(n= n(), 
                                                C1 = sum(C1_corr_dir),
                                                C1pc = sum(C1_corr_dir)/n()*100,
                                                C2 = sum(C2_B_inCI),
                                                C2pc = sum(C2_B_inCI)/n()*100,
                                                C3 = sum(C3_AB_pvalue),
                                                C3pc = sum(C3_AB_pvalue)/n()*100,
                                                C4 = sum(C4_dBIC_AB),
                                                C4pc = sum(C4_dBIC_AB)/n()*100,
                                                C3C4 = sum(C4_dBIC_AB&C3_AB_pvalue),
                                                C3C4pc = sum(C4_dBIC_AB&C3_AB_pvalue)/n()*100,
                                         allC = sum(C0_bAB& C4_dBIC_AB&C3_AB_pvalue),
                                                allC = sum(C0_bAB& C4_dBIC_AB&C3_AB_pvalue)/n()*100, .groups = 'drop')

fwrite(t, paste0(path_out_figures, "T3_", model_type, ".csv"))
fwrite(r, paste0(path_out_figures, "T2_", model_type, ".csv"))
fwrite(dR, paste0(path_out_figures, "AB_Summary", model_type, ".csv"))

table_out(dR$family, "Family")

table_out(table(dR$family, dR$C1_corr_dir), "Family & Condition C1", 0)

table_out(table(dR$family, dR$C3_AB_pvalue), "Family & Condition C1", 0)

table_out(table(dR$family, dR$C1C2C3C4), "Family & Condition C1&C2&C3&C4", 0)
```

```{r Figures and Tables}
#Creating Figures for BIC and correlations

dR<-dR[!is.na(dR$family),]


p <- ggplot(dR, aes(x=family, y=dBICA, color = family)) + 
  geom_violin(trim=FALSE)+
  xlab("") + ylab("BIC change") +
    geom_jitter(shape=16, position=position_jitter(0.3))+
  scale_fill_brewer(palette="RdBu") + 
  theme(axis.text.y = element_text(size = rel(1.1), angle = 90))+
  theme(axis.text.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.title.y = element_text(size = rel(1.1), angle = 90))+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey90"),
        axis.line = element_line(color= "grey"))
p<-p + guides(colour="none")
p
w_img=2000
h_img=2000
ggsave(paste0(path_out_figures, "F3_BIC_", model_type,".png"),width = w_img, height  = h_img, units = "px", dpi = 300 )

tmp<-dR %>% filter(measure == "-") %>% select(model)
#%>% filter(measure!="cor")
dR10 <-  dR  %>%
  arrange(dBICA) %>%
  group_by(family) %>%
  top_n(10)
#names(dR10)
p1 <- ggplot(dR10, aes(x=family, y=dBICA, color = family)) + 
  geom_violin(trim=FALSE)+
  xlab("") + ylab("BIC change") +
  geom_jitter(shape=16, position=position_jitter(0.3))+
  geom_text(aes(label = lmd_A), nudge_y=0.05, check_overlap = FALSE, size =0.8)+
  scale_fill_brewer(palette="RdBu") + 
theme(axis.text.y = element_text(size = rel(1.1), angle = 90))+
  theme(axis.text.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.title.y = element_text(size = rel(1.1), angle = 90))+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey90"),
        axis.line = element_line(color= "grey"))
p1<-p1 + guides(colour="none")

p1
ggsave(paste0(path_out_figures, "F4_BIC_top10_", model_type,".png"),width = w_img, height  = h_img,  units = "px", dpi = 300 )

dR$absCor<-abs(dR$corLDMmRT_A)

c <- ggplot(dR, aes(x=family, y=absCor, color = family)) + 
  geom_violin(trim=FALSE)+
  geom_jitter(shape=16, position=position_jitter(0.3))+
  xlab("") + ylab("Absolute Correlation") +
  scale_fill_brewer(palette="RdBu") +
 theme(axis.text.y = element_text(size = rel(1.1), angle = 90))+
  theme(axis.text.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.title.y = element_text(size = rel(1.1), angle = 90))+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey90"),
        axis.line = element_line(color= "grey"))

c<-c + guides(colour="none")

c
ggsave(paste0(path_out_figures, "F1_absCor_", model_type,".png"),width = w_img, height  = h_img,  units = "px", dpi = 300 )
cR10 <-  dR%>% select(model, family, absCor, lmd_A) %>% unique() %>%
  arrange(absCor) %>%
  group_by(family) %>%
  top_n(10)

cR10[order(cR10$absCor, decreasing = TRUE),]


c1 <- ggplot(cR10, aes(x=family, y=absCor, color = family)) + 
  geom_violin(trim=FALSE)+
  geom_jitter(shape=16, position=position_jitter(0.3))+
  geom_text(aes(label = lmd_A), nudge_y=0.05, check_overlap = TRUE)+
#  xlab("Model family")
  xlab("") +
  ylab("Absolute Correlation") +
  scale_fill_brewer(palette="RdBu") + 
  theme(axis.text.y = element_text(size = rel(1.1), angle = 90))+
  theme(axis.text.x = element_text(size = rel(1.3), angle = 0))+
  theme(axis.title.y = element_text(size = rel(1.1), angle = 90))+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey90"),
        axis.line = element_line(color= "grey"))
c1<-c1 + guides(colour="none")
c1
ggsave(paste0(path_out_figures,"F2_Cor_top10_", model_type,".png"),width = w_img, height  = h_img,  units = "px", dpi = 300 )
c<-c + guides(colour="none")



plot_grid(c,c1, align = "hv", ncol = 1, rel_heights = c(3/5, 2/5))
ggsave(paste0(path_out_figures, "F21_Cor_", model_type,".png"),width =2400, height  = 3200,  units = "px", dpi = 300 )

plot_grid(p,p1, align = "hv", ncol = 1, rel_heights = c(3/5, 2/5))
ggsave(paste0(path_out_figures, "F43_BIC_", model_type,".png"),width =2400, height  = 3200,  units = "px", dpi = 300 )

plot_grid(c,c1,p,p1, align = "hv", ncol = 2, rel_heights = c(1/2, 1/2), labels = c("a", "b", "c","d"))
ggsave(paste0(path_out_figures, "F5_COR_BIC", model_type,".png"),width =2400, height  = 3200,  units = "px", dpi = 300 )



```
## additional Figures
```{r}
min_BICf = -5#-5 for all
max_BICf = 31 #31 for all we compare with the best baseline with smallest BIC - ukwac
# remove misleading llms + 3 corpora (as it makes no sense)
```


```{r}
dRf<-dR[dR$family=="ngram", ]

dRf$model<-sub("_ngram", "", dRf$model)

#names(dRf)

p_ngram <- ggplot(dRf, aes(x=model, y=dBICA, color = corpora,  shape = window_radius)) + 
  geom_point(size = 3) +
  scale_shape_manual(values = c(1, 2, 5, 6 )) + 
  labs(x = "", 
       y= expression(Delta * "BIC"),
       title = "n-gram") +
#    geom_jitter(shape=16, position=position_jitter(0.3))+
  scale_fill_brewer(palette="RdBu") + 

    scale_color_manual(values = c("orange", "blue", "darkgreen")) +  # Three colors for three corpora levels
  #scale_color_gradient(low = "lightblue", high = "darkblue") +
   scale_y_continuous(limits = c(min_BICf, max_BICf)) +  # Y-axis from -10 to +10
  theme(axis.text.y = element_text(size = rel(1.1), angle = 90))+
  theme(axis.text.x = element_text(size = rel(1), angle = 00))+
  theme(axis.title.y = element_text(size = rel(1.1), angle = 90))+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey90"),
        axis.line = element_line(color= "grey"),
        plot.title = element_text(hjust = 0.5),
        plot.margin = margin(t = 10, r = 10, b = 50, l = 10, unit = "pt"),  # Increased bottom margin
        panel.grid.major = element_line(size = 0.5),
        panel.grid.minor = element_line(size = 0.25))
p_ngram

w_img=2000
h_img=2000
ggsave(paste0(path_out_figures,"/X1_BIC_ngram_", model_type,"_", min_BICf,"_", max_BICf, ".png"),width = w_img, height  = h_img, units = "px", dpi = 300 )
```

```{r}
# getBIC(d_BIC, "ukwac", "A") 
#ukwac best for baseline

dRl<-dR[dR$pretrained ==1 &  dR$corpora == "ukwac" , ]

nice_names<-rbind(c("dolphin_2_8_mistral_7b_v02_Q8_0", "mistral_g2-07B"),
c("glove_6B_300d", "GLoVE_06B"),
c("Hermes_3_Llama_3_1_70B_Q5_K_M", "llama_g3.1-70B"),
c("llama_2_13b_Q8_0", "llama_g2-13B" ),
c("llama_2_70b_Q5_0", "llama_g2-70B"),
c("llama_2_7b_Q8_0", "llama_g2-07B"),
c("llama_30b_Q8_0", "llama_g1-30B"),
c("llama_65b_Q5_0", "llama_g1-65B"),
c("llama_7b_Q8_0","llama_g1-07B"),
c("Meta_Llama_3_1_70B_Q5_K_M", "llama_g3.1-70B"),
c("meta_llama_3_1_8b_q8_0","llama_g3.1-08B"),
c("mistral_7b_v0_1_Q8_0", "mistral_g1-07B"),
c("Mistral_7B_v0_3_Q8_0", "mistral_g3-07B"))

for (i in (1:nrow(nice_names))){
  dRl$model<-gsub(nice_names[i,1], nice_names[i,2], dRl$model)
}

dRl <- sort_by(dRl, dRl$model)
table(dRl$model)

p_llms <- ggplot(dRl, aes(x=model, y=dBICA, color = measure,  shape = case)) + 
  geom_point(size = 3) +
  scale_shape_manual(values = c(7,0)) +  # Square, Circle, Filled Dot, Diamond
  labs(x = "", 
       y= expression(Delta * "BIC"),
       title = "LLMs and GLoVE") +
#    geom_jitter(shape=16, position=position_jitter(0.3))+
 # scale_fill_brewer(palette="RdBu") + 
  #scale_color_gradient(low = "lightgreen", high = "darkgreen") +
  scale_color_manual(values = c("yellow", "red","purple")) +  # Three colors for three measures levels
   scale_y_continuous(limits = c(min_BICf, max_BICf)) +  # Y-axis from -10 to +10
  theme(axis.text.y = element_text(size = rel(1.1), angle = 0))+
  theme(axis.text.x = element_text(size = rel(1.), angle = 90))+
  theme(axis.title.y = element_text(size = rel(1.1), angle = 90))+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey90"),
        axis.line = element_line(color= "grey"),
        plot.title = element_text(hjust = 0.5),
        plot.margin = margin(t = 10, r = 10, b = 50, l = 10, unit = "pt"),  # Increased bottom margin
        panel.grid.major = element_line(size = 0.5),
        panel.grid.minor = element_line(size = 0.25))
p_llms
w_img=2000
h_img=2000
ggsave(paste0(path_out_figures,"/X2_BIC_llms", model_type,min_BICf,"_", max_BICf,".png"),width = w_img, height  = h_img, units = "px", dpi = 300 )


```

```{r}
# getBIC(d_BIC, "ukwac", "A") 
#ukwac best for baseline

dRl<-dR[dR$family=="predict" & dR$measure=="cos",]
dRl$model<-sub("gram", "", dRl$model)
table(dRl$model)
dRl$model <- paste(dRl$model, dRl$embedding_size, sep = " ")

p_predict <- ggplot(dRl, aes(x=model, y=dBICA, color = corpora,  shape = window_radius)) + 
  geom_point(size = 3) +
  scale_shape_manual(values = c(1, 2, 5, 6 )) + 
  labs(x = "", 
       y= expression(Delta * "BIC"),
       title = "predict") +
#    geom_jitter(shape=16, position=position_jitter(0.3))+
 # scale_fill_brewer(palette="RdBu") + 
  #scale_color_gradient(low = "lightgreen", high = "darkgreen") +
  scale_color_manual(values = c("orange", "blue", "darkgreen")) +  # Three colors for three corpora levels
   scale_y_continuous(limits = c(min_BICf, max_BICf)) +  # Y-axis from -10 to +10
  theme(axis.text.y = element_text(size = rel(1.1), angle = 90))+
  theme(axis.text.x = element_text(size = rel(1), angle = 0))+
  theme(axis.title.y = element_text(size = rel(1.1), angle = 90))+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey90"),
        axis.line = element_line(color= "grey"),
        plot.title = element_text(hjust = 0.5),
        plot.margin = margin(t = 10, r = 10, b = 50, l = 10, unit = "pt"),  # Increased bottom margin
        panel.grid.major = element_line(size = 0.5),
        panel.grid.minor = element_line(size = 0.25))
p_predict
w_img=2000
h_img=2000
ggsave(paste0(path_out_figures,"/X2_BIC_predict", model_type,min_BICf,"_", max_BICf,".png"),width = w_img, height  = h_img, units = "px", dpi = 300 )


```
```{r}
# getBIC(d_BIC, "ukwac", "A") 
#ukwac best for baseline

dRl<-dR[dR$family=="count"& dR$pretrained==0 &  dR$measure == "cos", ]
table(dRl$model)
dRl$model<-sub("_None", "", dRl$model)
dRl$model<-sub("conditional", "cond", dRl$model)


p_count <- ggplot(dRl, aes(x=model, y=dBICA, color = corpora,  shape = window_radius)) + 
  geom_point(size = 3) +
  scale_shape_manual(values = c(1, 2, 5, 6 )) + 
  labs(x = "", 
       y= expression(Delta * "BIC"),
       title = "count") +
#
#    geom_jitter(shape=16, position=position_jitter(0.3))+
 # scale_fill_brewer(palette="RdBu") + 
  #scale_color_gradient(low = "lightgreen", high = "darkgreen") +
   scale_color_manual(values = c("orange", "blue", "darkgreen")) +  # Three colors for three corpora levels
   scale_y_continuous(limits = c(min_BICf, max_BICf)) +  # Y-axis from -10 to +10
  theme(axis.text.y = element_text(size = rel(1.1), angle = 0))+
  theme(axis.text.x = element_text(size = rel(0.8), angle = 0))+
  theme(axis.title.y = element_text(size = rel(1.1), angle = 90))+
  theme(panel.background = element_rect(fill = "white"),
        panel.grid = element_line(color = "grey90"),
        axis.line = element_line(color= "grey"),
        plot.title = element_text(hjust = 0.5),
        plot.margin = margin(t = 10, r = 10, b = 50, l = 10, unit = "pt"),  # Increased bottom margin
        panel.grid.major = element_line(size = 0.5),
        panel.grid.minor = element_line(size = 0.25))

p_count
w_img=2000
h_img=2000
ggsave(paste0(path_out_figures,"/X2_BIC_count", model_type,min_BICf,"_", max_BICf,".png"),width = w_img, height  = h_img, units = "px", dpi = 300 )


```
```{r}

# Combine the plots 
combined_plot <- p_ngram / p_count /p_predict / p_llms  +
  plot_layout(guides = "collect")+
  plot_annotation(tag_levels = "A")


# Display the combined plot
combined_plot

ggsave(paste0(path_out_figures,"/X5_4BIC_fig_", model_type,min_BICf,"_", max_BICf,".png"),width =2400, height  = 3200,  units = "px", dpi = 300 )
```
